On Misuses of the Kolmogorov–Smirnov-Test

### 2022-04-22 Manuscript/manuscript.tex

@@

\begin{abstract}
The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
often been misused. The standard one-sample KS test applies to independent, continuous 
data with a hypothesized distribution that is completely specified. It is not uncommon, 
however, to see in the literature that it was applied to dependent, discrete, or 
rounded data, with hypothesized distributions containing estimated parameters. 
For example, it has been “discovered” multiple times that the test is too conservative 
when the parameters are estimated. This paper aims to discuss misuses of the KS test, 
demonstrate their consequences through simulation, and provide remedies as needed.
\end{abstract}

@@

The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution. The test is 
performed as follows. Let $X_1, ..., X_n$ be i.i.d. random variables from $F_{n}(x)$,
the empirical cumulative distribution.
Let $F(x)$ be the population cumulative distribution. The K-S 
statistic is \[d = \max\lvert F_{n}(x) - F(x) \rvert\]. The null hypothesis 
is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
alternate hypothesis is that the data is not from $F(x)$. The table of critical 
values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected.

@@

\begin{itemize}
  \item 
    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator 
    of the distribution function $F_n$ based on the sample $X_1,...,X_n$
  \item 
    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
    of the sample $X_1,...,X_n$
  \item 
    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
    sample $X_1^*,...,X_n^*$
  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-F^*_n(x) \rvert)$
\end{itemize}

>>>>

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}

@@

\begin{abstract}
The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
often been misused. The standard one-sample KS test applies to independent, continuous 
data with a hypothesized distribution that is completely specified. It is not uncommon, 
however, to see in the literature that it was applied to dependent, discrete, or 
rounded data, with hypothesized distributions containing estimated parameters. 
For example, it has been “discovered” multiple times that the test is too conservative 
when the parameters are estimated \citep[e.g.,][]{Steinskog}. This paper aims to survey 
the misuses of the KS test, demonstrate their consequences through simulation, and 
provide remedies as needed.
\end{abstract}

@@

The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution. The test is 
performed as follows. Let $X_1, ..., X_n$ be i.i.d. random variables from $F_{n}(x)$,
the empirical cumulative distribution.
Let $F(x)$ be the population cumulative distribution. The K-S 
statistic is 
\[
  d = \max{\lvert F_{n}(x) - F(x) \rvert}.
\].
The null hypothesis is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
alternate hypothesis is that the data is not from $F(x)$. The table of critical 
values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected.

@@

\begin{itemize}
  \item 
    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator 
    of the distribution function $F_n$ based on the sample $X_1,...,X_n$
  \item 
    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
    of the sample $X_1,...,X_n$
  \item 
    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
    sample $X_1^*,...,X_n^*$
  \item Thus, the K-S statistic for each bootstrap case is $\max(\lvert F(x)-F^*_n(x) \rvert)$
\end{itemize}
